---
title: "Overview"
output:
  BiocStyle::html_document:
    toc: true
vignette: >
  % \VignetteIndexEntry{0: Overview}
  % \VignetteEngine{knitr::rmarkdown}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

```{r setup, echo=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

Authors: Martin Morgan (<a
  href="mailto:mtmorgan@fhcrc.org">mtmorgan@fhcrc.org</a>), Sonali
  Arora (<a
  href="mailto:sarora@fredhutch.org">sarora@fredhutch.org</a>)<br />
Date: 30 June, 2015

We start with an introductory presentation, and continue to a hands-on
practical.  The practical has three parts. Each part consists of
informative material followed by short or intermediate length
exercises and case studies. The material introduces or refreshes your
knowledge of _R_, and walks through some of the central classes and
annotation resources for working with high-throughput sequence data in
_Bioconductor_.

It's recommended that you choose two of the following sections, and
spend about 45 minutes on each. Take time to work through the code in
the material as well as the exercises, asking questions of your
colleagues and the TAs as needed. If you're relatively new to _R_,
then consider doing the first two sections. If you're new to
_Bioconductor_, then the second and either the third or fourth section
is recommended.

1. Presentation:
   [_R_ / _Bioconductor_ for Sequence Analysis](L1-rbioc-for-sequencing.pdf)

2. Lab: [Introduction to _Bioconductor_](L2-bioc-intro.html)

3. Lab: [Data Representations](L3-data-representation.html)

4. Lab: [Annotation](L4-annotation.html)

5. Lab: [Differential Expression](L5-differential-expression.html)
